---
title: "GIS_Coursework"
author: "Eleni Kalantzi"
date: 11/01/21
output: 
  html_document: default
  pdf_document: default
---
# **Τhe relationship between obesity and socioeconomic factors and its geographical variation per London borough**

## Installing the libraries:
```{r}
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(broom)
library(spgwr)
library(GWmodel)
library(spatialreg)
library(corrr)
library(corrplot)
source("http://www.sthda.com/upload/rquery_cormat.r")
```

## 1. Importing the shapefile for Analysis
```{r}
LondonBoroughs<-dir_info(here::here("statistical-gis-boundaries-london", 
                                 "ESRI"))%>%
  dplyr::filter(str_detect(path, 
                           "London_Borough_Excluding_MHW.shp$"))%>%
  dplyr::select(path)%>%
  pull()%>%
## read in the file in
  st_read()
qtm(LondonBoroughs)
```

## 2. Reading the OLS regression data:
```{r}
Datareg <- readxl::read_xlsx('overall.xlsx')
## basic statistics
summary(Datareg[3:8])
sd(Datareg$Percentage_with_no_qualifications_aged_25_64)
sd(Datareg$`Percentage_of _Obese_Children_in_Year_6`)
```

#### Merge boundaries and data:
```{r}
LonBoroughs <- LondonBoroughs%>%
  left_join(.,
            Datareg, 
            by = c("GSS_CODE" = "Borough Code"))
```

#### Visualise the independent variables to observe their spatial variation:
```{r}
tmap_mode("plot")
tm1 <- tm_shape(LonBoroughs) + 
  tm_polygons("Percentage_of _Obese_Children_in_Year_6", 
              style="jenks",
              palette="Reds")+
  tm_layout(main.title = "Chilhood Obesity in 2017-2018 per London Borough", main.title.position = "center", main.title.size = 1.4, legend.show=TRUE, legend.position=c("left","bottom"), legend.title.size = 0.8, legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm1
tmap_save(tm1, 'ChOb.png', dpi=300)
tm2 <- tm_shape(LonBoroughs) + 
  tm_polygons("Median_annual_income", 
              style="jenks",
              palette="Blues")+
  tm_layout(main.title = "Personal Income by Tax Year 2017-2018", main.title.position = "center", main.title.size = 1.3, legend.show=TRUE, legend.position=c("left","bottom"), legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm2
tmap_save(tm2, 'Med_Income.png', dpi=300)
tm3 <- tm_shape(LonBoroughs) + 
  tm_polygons("Population_per_square_km", 
              style="quantile",
              palette="YlOrRd")+
  tm_layout(main.title = "Population Density in 2018 per London Borough", main.title.position = "center", main.title.size = 1.1, legend.show=TRUE, legend.position=c("left","bottom"), legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm3
tmap_save(tm3, 'Density.png', dpi=300)
tm4 <- tm_shape(LonBoroughs) + 
  tm_polygons("Percentage_with_no_qualifications_aged_25_64", 
              style="quantile",
              palette="Purples")+
  tm_layout(main.title = "People aged 25-64 with no academic/professional qualifications in 2018", main.title.position = "center", main.title.size = 1.2, legend.show=TRUE, legend.position=c("left","bottom"), legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm4
tmap_save(tm4, 'Education.png', dpi=300)

tm5 <- tm_shape(LonBoroughs) + 
  tm_polygons("Percentage_of_homes_with_deficiency_in_access_to_nature", 
              style="quantile",
              palette="Greens")+
  tm_layout(main.title = "Percentage of homes located within open space and access to nature in 2012", main.title.position = "center", main.title.size = 1.1, legend.show=TRUE, legend.position=c("left","bottom"),legend.title.size = 0.8,
            legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm5
tmap_save(tm5, 'Nature.png', dpi=300)

tm6 <- tm_shape(LonBoroughs) + 
  tm_polygons("Fast_food_outlets_per_100_residents", 
              style="quantile",
              palette="RdPu")+
  tm_layout(main.title = "Density of fast food outlets at 02/07/2018", main.title.position = "center", main.title.size = 1.1, legend.show=TRUE, legend.position=c("left","bottom"),legend.title.size = 0.9,
            legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata Β© Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm6
tmap_save(tm6, 'Fast_Food.png', dpi=300)
```

### Run regression for model 1:
```{r}
model1 <- lm(LonBoroughs$`Percentage_of _Obese_Children_in_Year_6` ~ 
            LonBoroughs$Median_annual_income + 
            LonBoroughs$Percentage_with_no_qualifications_aged_25_64 + 
            LonBoroughs$Population_per_square_km + 
            LonBoroughs$Percentage_of_homes_with_deficiency_in_access_to_nature+
            LonBoroughs$Fast_food_outlets_per_100_residents)
summary(model1)
tidy(model1)
glance(model1)
```

### Histograms and transformations
#### We'll plot some histograms to check if the variables follow normal distribution:
```{r}
hist(LonBoroughs$`Percentage_of _Obese_Children_in_Year_6`, 
     main="Figure 2: A histogram of the distribution of the Childhood Obesity variable", 
     xlab="% of Obese Children in Year 6", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)
lines(density(LonBoroughs$`Percentage_of _Obese_Children_in_Year_6`), col="red", lwd=3)

hist(LonBoroughs$Median_annual_income, 
     main="Figure 3: A histogram of median annual income variable", 
     xlab="median annual income", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughs$Median_annual_income), col="red", lwd=3)

hist(LonBoroughs$Population_per_square_km, 
     main="Figure 6: A histogram of population density variable", 
     xlab="population per square km", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughs$Population_per_square_km), col="red", lwd=3)

hist(LonBoroughs$Percentage_with_no_qualifications_aged_25_64, 
     main="Figure 9: A histogram of people without qualifications variable", 
     xlab="% of people with no qualifications aged 25-64", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughs$Percentage_with_no_qualifications_aged_25_64), col="red", lwd=3)

hist(LonBoroughs$Percentage_of_homes_with_deficiency_in_access_to_nature, 
     main="Figure 10: A histogram of access to nature variable", 
     xlab="% of home with deficient access to nature", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughs$Percentage_of_homes_with_deficiency_in_access_to_nature), col="red", lwd=3)

hist(LonBoroughs$Fast_food_outlets_per_100_residents, 
     main="Figure 13: A histogram of density of Fast Food outlets variable", 
     xlab="Fast Food outlets per 100 residents", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughs$Fast_food_outlets_per_100_residents), col="red", lwd=3)
```

#### We'll use symbox to help us find the appropriate transformation:
```{r}
symbox(~`Percentage_of _Obese_Children_in_Year_6`, 
       LonBoroughs, 
       na.rm=T,
       powers=seq(-4,4,by=.5))

symbox(~Median_annual_income, 
       LonBoroughs, 
       na.rm=T,
       powers=seq(-4,4,by=.5))

symbox(~Population_per_square_km, 
       LonBoroughs, 
       na.rm=T,
       powers=seq(-4,4,by=.5))

symbox(~Percentage_of_homes_with_deficiency_in_access_to_nature, 
       LonBoroughs, 
       na.rm=T,
       powers=seq(-4,4,by=.5))

symbox(~Fast_food_outlets_per_100_residents, 
       LonBoroughs, 
       na.rm=T,
       powers=seq(-4,4,by=.5))
```

#### Transform data for new regression models:
```{r}
Data_reg_trans <- readxl::read_xlsx('trans_reg.xlsx')
## Merge transformed data and boundaries
LonBoroughstrans <- LondonBoroughs%>%
  left_join(.,
            Data_reg_trans, 
            by = c("GSS_CODE" = "Borough Code"))
```

#### Plot histograms of transformed variables:
```{r}
hist(LonBoroughstrans$`Median_annual_income _^-2.5`, 
     main="Figure 5: A histogram of (median annual income)^-2.5 variable", 
     xlab="(median annual income)^-2.5", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughstrans$`Median_annual_income _^-2.5`), col="red", lwd=3)

hist(LonBoroughstrans$log_Population_per_square_km, 
     main="Figure 8: A histogram of log population density variable", 
     xlab="log(population per square km)", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughstrans$log_Population_per_square_km), col="red", lwd=3)

hist((LonBoroughs$Percentage_of_homes_with_deficiency_in_access_to_nature)^-0.5, 
     main="Figure 12: A histogram of (access to nature)^-0.5 variable", 
     xlab="(% of home with deficient access to nature)^-0.5", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density((LonBoroughs$Percentage_of_homes_with_deficiency_in_access_to_nature)^-0.5), col="red", lwd=3)

hist(LonBoroughstrans$`Fast_food_outlets_per_100_residents_^-1`, 
     main="Figure 15: A histogram of density of (Fast Food outlets)^-1 variable", 
     xlab="(Fast Food outlets per 100 residents)^-1", 
     border="black", 
     col="white",
     las=1, 
     breaks=20, 
     freq = FALSE)

lines(density(LonBoroughstrans$`Fast_food_outlets_per_100_residents_^-1`), col="red", lwd=3)
```

### Run regression for model 2:
```{r}
model2 <- lm(Data_reg_trans$`Percentage_of _Obese_Children_in_Year_6` ~ 
              Data_reg_trans$`Median_annual_income _^-2.5` + 
              Data_reg_trans$Percentage_with_no_qualifications_aged_25_64 + 
              Data_reg_trans$log_Population_per_square_km + 
              Data_reg_trans$Percentage_of_homes_with_deficiency_in_access_to_nature +
              Data_reg_trans$`Fast_food_outlets_per_100_residents_^-1`)
summary(model2)
tidy(model2)
glance(model2)
```
#### We'll exclude the statistically insignificant variable and re-run the regression.

### Run regression for model 3:
```{r}
model3 <- lm(Data_reg_trans$`Percentage_of _Obese_Children_in_Year_6` ~ 
              Data_reg_trans$`Median_annual_income _^-2.5` + 
              Data_reg_trans$log_Population_per_square_km + 
              Data_reg_trans$Percentage_of_homes_with_deficiency_in_access_to_nature +
              Data_reg_trans$`Fast_food_outlets_per_100_residents_^-1`)
summary(model3)
tidy(model3)
glance(model3)
```

### Regression Assumptions for model 3:
#### a. Plot regression fit line
```{r}
q <- qplot(x = `Median_annual_income _^-2.5`, 
           y = `Percentage_of _Obese_Children_in_Year_6`, 
           data=LonBoroughstrans)
q + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()
q1 <- qplot(x = log_Population_per_square_km, 
           y = `Percentage_of _Obese_Children_in_Year_6`, 
           data=LonBoroughstrans)
q1 + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()
q2 <- qplot(x = Percentage_of_homes_with_deficiency_in_access_to_nature, 
           y = `Percentage_of _Obese_Children_in_Year_6`, 
           data=LonBoroughstrans)
q2 + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()
q3 <- qplot(x = `Fast_food_outlets_per_100_residents_^-1`, 
           y = `Percentage_of _Obese_Children_in_Year_6`, 
           data=LonBoroughstrans)
q3 + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()
```

#### b. Check the residuals into our dataframe
```{r}
# Save the residuals into our dataframe
model_data <- model3 %>%
  augment(., Data_reg_trans)
# Add them to the shapelayer
LonBoroughstrans <- LonBoroughstrans %>%
  mutate(model3resids = residuals(model3))
# Plot residuals to see if they follow normal distribution
model_data%>%
  dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
  geom_histogram(bins=30)
```

#### c. Visualisation of the correlation matrix
```{r}
# library corrplot + rquery.cormat
rquery.cormat(Data_reg_trans[4:7], type='full',
              graph=TRUE, graphType="correlogram")
vif(model1)
vif(model2)
vif(model3)
```

#### d. Print some model diagnositcs for homoscedasticity
```{r}
par(mfrow=c(2,2))    
#plot to 2 by 2 array
plot(model3)
```

#### e.Independence of errors
```{r}
# Standard autocorrelation: run durbin-watson test
DW <- durbinWatsonTest(model3)
tidy(DW)
# Plot the residuals to check spatial autocorrelation
tmap_mode("plot")

tm_res <- tm_shape(LonBoroughstrans) +
  tm_polygons("model3resids", palette = "RdYlBu")+
tm_layout(main.title = "Map of residuals of Model 3", main.title.position = "center", main.title.size = 1.4, 
          legend.show=TRUE, legend.position=c("left","bottom"), legend.title.size = 0.9, legend.frame=TRUE)+
  tm_scale_bar(position=c("right", "top"), text.size=0.6)+
  tm_compass(north=0,type="8star", position=c("left", "top"))+
  tm_credits("Contains National Statistics\nand Ordnance Survey\ndata © Crown copyright\nand database right [2015]\nDepartment: CASA-UCL\nCourse:GIS, Professors:\nA.Denett & A.Maclachlan\nCreated by: Eleni Kalantzi\nDate: 27/12/20", position=c("right", "bottom"))
tm_res
tmap_save(tm_res, 'Static_resid_3.png', dpi=300)
```

#### Start calculating Moran's I:
```{r}
# Calculate the centroids of all Boroughs in London
coordsB <- LondonBoroughs%>%
  st_centroid()%>%
  st_geometry()

plot(coordsB,axes=TRUE)

# create a neighbours list
LB_nb <- LonBoroughstrans %>%
  poly2nb(., queen=T)

# and 4 nearest neighbours
knn_boroughs <-coordsB %>%
  knearneigh(., k=4)
LB_knn <- knn_boroughs %>%
  knn2nb()

# then plot them
plot(LB_nb, st_geometry(coordsB), col="red")
plot(LondonBoroughs$geometry, add=T)
plot(LB_knn, st_geometry(coordsB), col="blue")
plot(LondonBoroughs$geometry, add=T)

# Create a spatial weights matrix object from these weights

LB.queens_weight <- LB_nb %>%
  nb2listw(., style="C")

LB.knn_4_weight <- LB_knn %>%
  nb2listw(., style="C")

LB.knn_4_weight
LB.queens_weight

# Moran's I for Queen and Knn4 for residuals
Queen <- LonBoroughstrans %>%
  st_drop_geometry()%>%
  dplyr::select(model3resids)%>%
  pull()%>%
  moran.test(., LB.queens_weight)%>%
  tidy()
Nearest_neighbour <- LonBoroughstrans %>%
  st_drop_geometry()%>%
  dplyr::select(model3resids)%>%
  pull()%>%
  moran.test(., LB.knn_4_weight)%>%
  tidy()
Queen
Nearest_neighbour

# Moran's I for model 3
lm.morantest(model3, LB.knn_4_weight)
lm.morantest(model3, LB.queens_weight)
```

## 3. Spatial Regression models
#### We'll run regression for Spatial lag model first:
```{r}
# Spatial lag model for queen
slag_dv_model3_queen <- lagsarlm(`Percentage_of _Obese_Children_in_Year_6` ~ `Median_annual_income _^-2.5` + 
                                   log_Population_per_square_km +
                                   Percentage_of_homes_with_deficiency_in_access_to_nature +
                                   `Fast_food_outlets_per_100_residents_^-1`,
                                  data = LonBoroughstrans,
                                  tol.solve=4.39317e-27,
                                  nb2listw(LB_nb, style="C"),
                                  method = "eigen")
tidy(slag_dv_model3_queen)
glance(slag_dv_model3_queen)
summary(slag_dv_model3_queen)
## Spatial lag model for knn-4
slag_dv_model3_knn4 <- lagsarlm(`Percentage_of _Obese_Children_in_Year_6` ~ `Median_annual_income _^-2.5` + 
                                  log_Population_per_square_km +
                                  Percentage_of_homes_with_deficiency_in_access_to_nature +
                                  `Fast_food_outlets_per_100_residents_^-1`,
                                 data = LonBoroughstrans,
                                 tol.solve = 2.46661e-27,
                                 nb2listw(LB_knn, style="C"), 
                                 method = "eigen")
tidy(slag_dv_model3_knn4)
glance(slag_dv_model3_knn4)
summary(slag_dv_model3_knn4)
```

#### We'll check the residuals:
```{r}
# Residuals from spatial lag model
LonBoroughstrans <- LonBoroughstrans %>%
  mutate(slag_dv_model3_knn_resids = residuals(slag_dv_model3_knn4))

KNN4Moran <- LonBoroughstrans %>%
  st_drop_geometry()%>%
  dplyr::select(slag_dv_model3_knn_resids)%>%
  pull()%>%
  moran.test(., LB.knn_4_weight)%>%
  tidy()

KNN4Moran

LonBoroughstrans <- LonBoroughstrans %>%
  mutate(slag_dv_model3_queen_resids = residuals(slag_dv_model3_queen))

QueenMoran <- LonBoroughstrans %>%
  st_drop_geometry()%>%
  dplyr::select(slag_dv_model3_queen_resids)%>%
  pull()%>%
  moran.test(., LB.queens_weight)%>%
  tidy()

QueenMoran
```

#### Then, we'll run Spatial Error Model:
```{r}
# SEM for Queen
SEM_model3_queen <- errorsarlm(`Percentage_of _Obese_Children_in_Year_6` ~ `Median_annual_income _^-2.5` + 
                                 log_Population_per_square_km +
                                 Percentage_of_homes_with_deficiency_in_access_to_nature +
                                 `Fast_food_outlets_per_100_residents_^-1`,
                                  data = LonBoroughstrans,
                                  tol.solve = 3.19139e-27,
                                 nb2listw(LB_nb, style="C"),
                                 method = "eigen")
tidy(SEM_model3_queen)
glance(SEM_model3_queen)
summary(SEM_model3_queen)
## SEM for KNN4
SEM_model3_knn4 <- errorsarlm(`Percentage_of _Obese_Children_in_Year_6` ~ `Median_annual_income _^-2.5` + 
                                log_Population_per_square_km +
                                Percentage_of_homes_with_deficiency_in_access_to_nature +
                                `Fast_food_outlets_per_100_residents_^-1`,
                              data = LonBoroughstrans,
                              tol.solve = 3.19139e-27,
                               nb2listw(LB_knn, style="C"),
                               method = "eigen")
tidy(SEM_model3_knn4)
glance(SEM_model3_knn4)
summary(SEM_model3_knn4)
```

## 4. GWR model
```{r}
# Set projections
st_crs(LonBoroughstrans) = 27700
LonBoroughsSPtrans <- LonBoroughstrans %>%
  as(., "Spatial")
st_crs(coordsB) = 27700
coordsBSP <- coordsB %>%
  as(., "Spatial")
coordsBSP

# calculate bandwitch
GWRbandwidthtrans <- gwr.sel(Percentage_of._Obese_Children_in_Year_6 ~ Median_annual_income._..2.5 + 
                          log_Population_per_square_km +
                          Percentage_of_homes_with_deficiency_in_access_to_nature +
                          Fast_food_outlets_per_100_residents_..1,
                        data = LonBoroughsSPtrans, 
                        coords=coordsBSP,
                        adapt=T)
GWRbandwidthtrans

# run the GWR model
gwr.modeltrans = gwr(Percentage_of._Obese_Children_in_Year_6 ~ Median_annual_income._..2.5 + 
                       log_Population_per_square_km +
                       Percentage_of_homes_with_deficiency_in_access_to_nature +
                       Fast_food_outlets_per_100_residents_..1,
                  data = LonBoroughsSPtrans,
                coords=coordsBSP,
                adapt=GWRbandwidthtrans,
                hatmatrix = TRUE,
                se.fit = TRUE)
```

#### Let's print the results of the GWR model:
```{r}
gwr.modeltrans
resultstrans <- as.data.frame(gwr.modeltrans$SDF)
names(resultstrans)
```

#### Moran's I for GWR:
```{r}
gwr.morantest(gwr.modeltrans, LB.queens_weight)
gwr.morantest(gwr.modeltrans, LB.knn_4_weight)
```

#### Monte Carlo approach:
```{r}
res.mont <- gwr.montecarlo(Percentage_of._Obese_Children_in_Year_6 ~ Median_annual_income._..2.5 + 
                             log_Population_per_square_km +
                             Percentage_of_homes_with_deficiency_in_access_to_nature +
                             Fast_food_outlets_per_100_residents_..1,
                           data = LonBoroughsSPtrans, bw = 30, adaptive = TRUE,
                          nsims = 95, kernel="gaussian")
bw <- bw.gwr(Percentage_of._Obese_Children_in_Year_6 ~ Median_annual_income._..2.5 + 
         log_Population_per_square_km +
         Percentage_of_homes_with_deficiency_in_access_to_nature +
         Fast_food_outlets_per_100_residents_..1,
       data = LonBoroughsSPtrans,
       approach = "AIC", kernel="gaussian")
res.mont
bw
```

#### Attach coefficients to original SF and plot them:
```{r}
LonBoroughs2 <- LonBoroughstrans %>%
  mutate(coefMedinc = resultstrans$Median_annual_income._..2.5,
         coefPopdens = resultstrans$log_Population_per_square_km ,
         coefaccnat = resultstrans$Percentage_of_homes_with_deficiency_in_access_to_nature,
         coeffastfood = resultstrans$Fast_food_outlets_per_100_residents_..1)
tmap_mode("view")
tm_shape(LonBoroughs2) +
  tm_polygons(col = "coefMedinc", palette = "RdBu", alpha = 0.6)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "coefPopdens", palette = "RdBu", alpha = 0.6)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "coefaccnat", palette = "RdBu", alpha = 0.6)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "coeffastfood", palette = "RdBu", alpha = 0.6, midpoint = NA)
```

#### Run the significance test:
```{r}
sigTest1 = abs(gwr.modeltrans$SDF$Median_annual_income._..2.5)-2 * gwr.modeltrans$SDF$Median_annual_income._..2.5_se
sigTest2 = abs(gwr.modeltrans$SDF$log_Population_per_square_km)-2 * gwr.modeltrans$SDF$log_Population_per_square_km_se
sigTest3 = abs(gwr.modeltrans$SDF$Percentage_of_homes_with_deficiency_in_access_to_nature)-2 * gwr.modeltrans$SDF$Percentage_of_homes_with_deficiency_in_access_to_nature_se
sigTest4 = abs(gwr.modeltrans$SDF$Fast_food_outlets_per_100_residents_..1)-2 * gwr.modeltrans$SDF$Fast_food_outlets_per_100_residents_..1_se
```

#### Finally, let's plot significance results:
```{r}
tmap_mode("view")
LonBoroughs2 <- LonBoroughs2 %>%
  mutate(GWRMedincSig = sigTest1)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "GWRMedincSig", palette = "RdYlBu", alpha = 0.6)
LonBoroughs2 <- LonBoroughs2 %>%
  mutate(GWRPopdensSig = sigTest2)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "GWRPopdensSig", palette = "RdYlBu", alpha = 0.6)
LonBoroughs2 <- LonBoroughs2 %>%
  mutate(GWRAccNatSig = sigTest3)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "GWRAccNatSig", palette = "RdYlBu", alpha = 0.6)
LonBoroughs2 <- LonBoroughs2 %>%
  mutate(GWRFastFoodSig = sigTest4)
tm_shape(LonBoroughs2) +
  tm_polygons(col = "GWRFastFoodSig", palette = "RdYlBu", alpha = 0.6)
sigTest1
sigTest2
sigTest3
sigTest4
```

